Simulating an Isolated Dwarf Galaxy with Individual Star Feedback and Chemistry

### 2018-03-13 main.tex
Update on Overleaf.

Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution. Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models. There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}. These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .

@@

%mm2 I think there does need to be some introduction to this discussion:
However, much of this work has been done with Lagrangian smoothed particle hydrodynamics (SPH) schemes, with a few recent exceptions  \citep{Few2012,Few2014,Vorobyov2015}. In its original form, SPH does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution. This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possibly models that are not necessarily applicable in every regime \citep[see ][]{Revaz2016}. While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution or additional viscosity to reduce. Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}. Moreover, metal mixing efficiencies may vary species-by-species, as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}. Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of 
the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however. The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.

@@

@@

Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy. We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for \ion{H}{1} self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}. We assume \ion{He}{1} ionization generally follows \ion{H}{1}. This allows us to approximate \ion{He}{1} self-shielding using the same form (A. Rahmati, private communication). We ignore \ion{He}{2} photoionization from the UV background entirely. Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from Cloudy (see Section 4.1.1 of \citet{Hu2017}). As mentioned previously, we have re-computed metal line cooling tables using \texttt{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription. This is described in more detail in Appendix ~\ref{appendix:cooling}.

@@

The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential. The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
\begin{equation}
\rho_{\rm gas} (R,z) = \frac{M_{\rm gas}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
\end{equation}
where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm gas}$ is approximately 70\% of the total gas mass. We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and a total gas mass of $M_{\rm T,gas} = 2.0\times 10^6$~M$_{\odot}$. We adopt a \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$, $R_{\rm vir}~=~27.4$~kpc and r$_{\rm s} = 990$~pc. This gives a maximum circular velocity $V_{\rm max} = 30.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~3.2$~kpc. These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties within the halo mass expected for galaxies of this size \citep{Ferrero2012}. We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in future work.

@@

@@

Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging. For Leo P, located at 1.7~Mpc, \ion{H}{1} observations that are capable of detecting the diffuse \ion{H}{1} throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest \ion{H}{1} clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.

@@

The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors on order of 100--1000 \citep{Muratov2015}. However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}. In Figure~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy. We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
\begin{equation} \label{eq:dotM}
\dot{M}_{\rm out} = \sum M_{\rm gas} \times v_{\rm r} / dL.
\end{equation} 
We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.

@@

\subsubsection{Metal Enriched Outflows}
Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}. This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Angles-Alcazar2017,Muratov2017}. In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}. The parameter used to quantify metal outflow efficiencies varies among works. Here, we define the metal mass loading factor as
\begin{equation} \label{eq:eta-metal}
\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times \frac{M_{\rm metal}}{M_{*}}},
\end{equation}
where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars. We note the very large loading factors in the first 20~Myr are artificial, and a byproduct of the initial conditions. For half of the evolution, the inner three radii give $\eta_{\rm metal}$ below unity (around 0.6), but it increases at each radius, fluctuating around unity for the second half of the simulation. Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}. \cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity. Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
\includegraphics[width=0.9\linewidth]{metal_fraction_evolution}
\caption{Top: Metal mass loading factor (see Eq.~\ref{eq:eta-metal}) at radii of 0.1 ({\em black}), 0.2 ({\em purple}), 0.5 ({\em salmon pink}), and 1.0 $R_{\rm vir}$ ({\em yellow}) over time. Bottom: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time. In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
\label{fig:metal_evolution}
\end{figure}

@@

\subsubsection{Metal Distribution within the ISM}
\textbf{CHANGE: Simplified plot to just log(N/O) to make this less confusing and easier to interpret. Cleaned up text accordingly.}
It is important to understand how metals from each source of stellar yields enrich the ISM. Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}. This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed. Therefore, either metals are transported first through a hot phase with high sound speed, or through efficient turbulent mixing within the ISM \citep[e.g.][]{Tassis2008,YangKrumholz2012}. It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species. It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few \ion{H}{1}I regions for a detailed examination.

@@

@@

\item Formation of a significant amount of H$_2$ through gas phase reactions with H$^-$. This dense gas is more resistive to feedback driven outflows than the less dense gas in the galaxy. This leads to high molecular gas fractions, with an H$_2$ mass comparable to that of \ion{H}{1} by the end of the simulation. This result requires further investigation to determine if this behavior is universally true of ultrafaint dwarf galaxies. See Figure~\ref{fig:ISM_evolution}.
\end{enumerate}

Finally, we used O and N as examples to briefly demonstrate that there are discernible differences in how individual metal species are distributed within the ISM of our galaxy. In future work we will investigate in detail how metal enrichment proceeds in low mass dwarf galaxies, including how metals move through the various phases of the ISM into star forming gas, and how individual metals move into halos. This will allow us to examine
the role that each source of feedback plays in driving dwarf galaxy chemodynamics.

\section*{Acknowledgements:} A.E. is funded by the NSF Graduate Research Fellowship DGE 16-44869. G.L.B. is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955. We gratefully recognize computational
resources provided by NSF XSEDE through grant number TGMCA99S024, by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center, Columbia University, and the Flatiron Institute. Analysis in this work
made significant use of the publicly available \textsc{yt} (http://ytproject.org)
toolkit. \textsc{Enzo}, \textsc{Grackle}, and \textsc{yt} are the products of a collaborative effort of many independent scientists from numerous institutions around
the world. Their commitment to open science has helped make
this work possible. We would also like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B. Cote, S. Glover, K. Hawkins, C. Hu, K. Johnston, B. O'Shea, M. Putman, B. Smith, J. Wall, and J. Wise.

\textit{Software:} \textsc{Enzo} \citep{Enzo2014}, \textsc{yt} \citep{yt}, \textsc{Grackle} \citep{GrackleMethod}, \textsc{Cloudy} \citep{Cloudy2013}, matplotlib, astropy
%\bibliographystyle{apj}
%\bibliography{msbib}

@@

\setcounter{figure}{0}
\section{Resolution Study}
\label{appendix:resolution_study}
\textbf{CHANGE: Updated plots with full runs. No significant change to text.}
We demonstrate the effect of varying resolution on three different results in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}, comparing the star formation rate, mass evolution, and metal ejection/retention fractions between high resolution simulations, two runs at 3.6 pc with different initial SN driving rates, and a final run at 7.2 pc. The physics in each of these simulations remains the same with the exception of our star formation threshold. Since star formation is set to occur at gas densities where the Jeans mass is unresolved at the maximum resolution, our star formation algorithm is tied to resolution. A factor of two decrease in resolution translates to a factor of four decrease in the star formation density threshold, from 200~cm$^{-3}$ in our fiducial runs, to 50~cm$^{-3}$ and 12.5~cm$^{-3}$ in our 3.6~pc and 7.2~pc resolution runs respectively.

>>>>

Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution. Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models. There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}. These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .

@@

%mm2 I think there does need to be some introduction to this discussion:
However, much of this work has been done with Lagrangian smoothed particle hydrodynamics (SPH) schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}. In its original form, SPH does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution. This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possibly models that are not necessarily applicable in every regime \citep[see ][]{Revaz2016}. While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution or additional viscosity to reduce. Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}. Moreover, metal mixing efficiencies may vary species-by-species, as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}. Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of 
the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however. The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.

@@

%
% KVJ: Possibly include a discussion on uncertainties in stellar yields
%

@@

Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}. We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for \ion{H}{1} self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}. We assume \ion{He}{1} ionization generally follows \ion{H}{1}. This allows us to approximate \ion{He}{1} self-shielding using the same form (A. Rahmati, private communication). We ignore \ion{He}{2} photoionization from the UV background entirely. Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from Cloudy (see Section 4.1.1 of \citet{Hu2017}). As mentioned previously, we have re-computed metal line cooling tables using \texttt{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription. This is described in more detail in Appendix ~\ref{appendix:cooling}.

@@

The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential. The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
\begin{equation}
\rho_{\rm gas} (R,z) = \frac{M_{\rm o}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
\end{equation}
where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm o}$ is approximately 70\% of the total gas mass. We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and $M_o = 1.26\times 10^6$~M$_{\odot}$. We adopt a \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$, $R_{\rm vir}~=~27.4$~kpc and r$_{\rm s} = 990$~pc. This gives a maximum circular velocity $V_{\rm max} = 30.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~3.2$~kpc. These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties within the halo mass expected for galaxies of this size \citep{Ferrero2012,Read2017}. We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in future work.

@@

{\bf New (addressing KVJ's comment to clarify how to interpret / what is target comparison point for our galaxy model:} We emphasize here that our model, with no initial stellar distribution, is not intended to reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales. In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations. Otherwise, the galaxy chemical properties would be dominated by the somewhat arbitrary choice of initial abundances. In some ways this is similar to the first pollution of pristine gas in the early Universe, but we note that we cannot directly make this comparison as the environmental conditions and UVB properties were different at high redshift, and we explicitly ignore Pop III and Pop II stellar evolution. Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe. The subsequent metal enrichment from the stars in our simulation can be thought of as a change in abundances, or delta abundances, from arbitrary initial conditions. We discuss how to make proper comparison to observed stellar and gas abundance properties of dwarf galaxies in future work, where we investigate the abundance evolution of our simulations in more detail.

@@

Constraining the gas scale height in ultra-faint dwarf galaxies observationally, to compare to our simulations, is challenging. For Leo P, located at 1.7~Mpc, \ion{H}{1} observations that are capable of detecting the diffuse \ion{H}{1} throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest \ion{H}{1} clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.

@@

The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors ($\eta = \dot{M}_{\rm out}/<\rm{SFR}>$) on order of 100--1000 \citep{Muratov2015}. However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}. In Figure~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy. We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
\begin{equation} \label{eq:dotM}
\dot{M}_{\rm out} = \sum M_{\rm gas} \times v_{\rm r} / dL.
\end{equation} 
We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.

@@

\subsubsection{Metal Enriched Outflows}
Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}. This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}. In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}. The parameter used to quantify metal outflow efficiencies varies among works. Here, we define the metal mass loading factor as the metal outflow rate divided by the metal production rate, or
\begin{equation} \label{eq:eta-metal}
\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times \frac{M_{\rm metal}}{M_{*}}},
\end{equation}
where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars. We note the very large loading factors in the first 20~Myr are artificial, and a byproduct of the initial conditions. For half of the evolution, the inner three radii give $\eta_{\rm metal}$ below unity (around 0.6), but it increases at each radius, fluctuating around unity for the second half of the simulation. Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}. \cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity. Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
\includegraphics[width=0.9\linewidth]{metal_fraction_evolution}
\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Figure~\ref{fig:mass_outflow}. This is the ratio between the metal outflow rate and the metal production rate. {\bf Bottom}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time. In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
\label{fig:metal_evolution}
\end{figure}

@@

\subsubsection{Differential Mixing of Elements Within the ISM}
\textbf{CHANGE: Simplified plot to just log(N/O) to make this less confusing and easier to interpret. Cleaned up text accordingly.}
It is important to understand how metals from each source of stellar yields enrich the ISM. Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}. This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed. Therefore, either metals are transported first through a hot phase with high sound speed, or through efficient turbulent mixing within the ISM \citep[e.g.][]{Tassis2008,YangKrumholz2012}. It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species. It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few \ion{H}{1}I regions for a detailed examination.

@@

{\bf New (response to KVJ comment on comparability):} As noted in Section~\ref{sec:IC}, our galaxy model is not intended to directly reproduce the observed properties of Local Group UFD's. Notably, our initial conditions neglect a pre-existing stellar population and are only followed for 500~Myr, a fraction of the age of z = 0 dwarf galaxies. However, we can still place our model in context with observations using simple comparisons to the star formation rate (Section~\ref{sec:gas_sf}), molecular gas (Section~\ref{sec:molecular gas content}), and metal retention fraction (Section~\ref{sec:obs_metals}) properties of observed dwarf galaxies. We show that these properties are broadly consistent with observations.

@@

\item (\textbf{Possibly remove depending on follow up}) Formation of a significant amount of H$_2$ through gas phase reactions with H$^-$. This dense gas is more resistive to feedback driven outflows than the less dense gas in the galaxy. This leads to high molecular gas fractions, with an H$_2$ mass comparable to that of \ion{H}{1} by the end of the simulation. This result requires further investigation to determine if this behavior is universally true of ultrafaint dwarf galaxies. See Figure~\ref{fig:ISM_evolution}.

\item Finally, we used O and N as examples to briefly demonstrate that there are discernible differences in how individual metal species are distributed within the ISM of our galaxy. These variations could be tied to differences in yield sources among elements (for example, AGB winds vs. SNe), as suggested by \cite{KrumholzTing2018}. This will be explored in more detail in future work (Emerick et. al. \textit{in prep.}).
\end{enumerate}

%In future work we will investigate in detail how metal enrichment proceeds in low mass dwarf galaxies, including how metals move through the various phases of the ISM into star forming gas, and how individual metals move into halos. This will allow us to examine the role that each source of feedback plays in driving dwarf galaxy chemodynamics.

\section*{Acknowledgements:} A.E. is funded by the NSF Graduate Research Fellowship DGE 16-44869. G.L.B. is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955. We gratefully recognize computational
resources provided by NSF XSEDE through grant number TGMCA99S024, by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center, Columbia University, and the Flatiron Institute. This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{matplotlib}, \textsc{hdf5}, \textsc{h5py}, \textsc{astropy}, \textsc{Cloudy} and \textsc{deepdish}. These are the products products of a collaborative effort of many independent developers from numerous institutions around the world. Their commitment to open science has helped make this work possible. We would also like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B. Cote, S. Glover, K. Hawkins, C. Hu, K. Johnston, B. O'Shea, M. Putman, B. Smith, J. Wall, and J. Wise.

%\textit{Software:} \textsc{Enzo} \citep{Enzo2014}, \textsc{yt} \citep{yt}, \textsc{Grackle} \citep{GrackleMethod}, \textsc{Cloudy} \citep{Cloudy2013}
%\bibliographystyle{apj}
%\bibliography{msbib}

@@

\setcounter{figure}{0}
\section{Resolution Study}
\label{appendix:resolution_study}

\textbf{CHANGE: Updated plots with full runs. No significant change to text.}
We demonstrate the effect of varying resolution on three different results in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}, comparing the star formation rate, mass evolution, and metal ejection/retention fractions between high resolution simulations, two runs at 3.6 pc with different initial SN driving rates, and a final run at 7.2 pc. The physics in each of these simulations remains the same with the exception of our star formation threshold. Since star formation is set to occur at gas densities where the Jeans mass is unresolved at the maximum resolution, our star formation algorithm is tied to resolution. A factor of two decrease in resolution translates to a factor of four decrease in the star formation density threshold, from 200~cm$^{-3}$ in our fiducial runs, to 50~cm$^{-3}$ and 12.5~cm$^{-3}$ in our 3.6~pc and 7.2~pc resolution runs respectively.
